Approximation as Differentiation: Notes

### 2025-05-24 main/formal-structures.tex
Also cite vákár22.
Cancel \prod override.

We take an approach based on the CHAD (Combinatory Homomorphic Automatic Differentiation) of Mattias Vákár and others \cite{nunes2023}. Here follows a rough overview of this approach and how we have applied it to Galois program slicing. \todo{Final version shouldn't be ``rough''!}

@@

\begin{definition}[Semi-additive category]
\label{def:biproducts:semi-additive}
A category with finite products and coproducts is \emph{semi-additive} if the canonical morphisms (projections
and injections) give an isomorphism
\[\textstyle X \coprod Y \iso X \prod Y\] that is natural in both variables.
\end{definition}

>>>>

We take an approach based on the CHAD (Combinatory Homomorphic Automatic Differentiation) of Mattias Vákár and others~\cite{vákár22,nunes2023}. Here follows a rough overview of this approach and how we have applied it to Galois program slicing. \todo{Final version shouldn't be ``rough''!}

@@

\begin{definition}[Semi-additive category]
\label{def:biproducts:semi-additive}
A category with finite products and coproducts is \emph{semi-additive} if the canonical morphisms (projections
and injections) give an isomorphism
\[\textstyle X \coprod Y \iso X \times Y\] that is natural in both variables.
\end{definition}
